% !TEX TS-program = xelatex
% !TEX encoding = UTF-8 Unicode
% -*- coding: UTF-8; -*-
% vim: set fenc=utf-8

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% SIMPLE-RESUME-CV
%% <https://github.com/zachscrivena/simple-resume-cv>
%% This is free and unencumbered software released into the
%% public domain; see <http://unlicense.org> for details.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% See "README.md" for instructions on compiling this document.

\documentclass[letterpaper,MMMyyyy,nonstopmode]{simpleresumecv}
% Class options:
% a4paper, letterpaper, nonstopmode, draftmode
% MMMyyyy, ddMMMyyyy, MMMMyyyy, ddMMMMyyyy, yyyyMMdd, yyyyMM, yyyy

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% PREAMBLE.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% CV Info (to be customized).
\newcommand{\CVAuthor}{Brandon Dean}
\newcommand{\CVTitle}{Brandon Dean's Resume}
\newcommand{\CVNote}{CV compiled on {\today}}
\newcommand{\CVWebpage}{deanbr.io}

% PDF settings and properties.
\hypersetup{
pdftitle={\CVTitle},
pdfauthor={\CVAuthor},
pdfsubject={\CVWebpage},
pdfcreator={XeLaTeX},
pdfproducer={},
pdfkeywords={},
unicode=true,
bookmarks=true,
bookmarksopen=true,
pdfstartview=FitH,
pdfpagelayout=OneColumn,
pdfpagemode=UseOutlines,
hidelinks,
breaklinks}

% Shorthand.
\newcommand{\Code}[1]{\mbox{\textbf{#1}}}
\newcommand{\CodeCommand}[1]{\mbox{\textbf{\textbackslash{#1}}}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% ACTUAL DOCUMENT.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%%%%%%%%%%%%%%%
% TITLE BLOCK %
%%%%%%%%%%%%%%%

\Title{Brandon Dean}

\begin{SubTitle}
{Software Engineer}
\par
{brdean77@gmail.com}
-
(804)\,385-6499
-
{\url{\CVWebpage}}
\end{SubTitle}

\begin{Body}

%%%%%%%%%%%%
%% SKILLS %%
%%%%%%%%%%%%

\Section
{Skills}
{Skills}
{PDF:Skills}

\begin{large}
\Entry
Java,
Ruby on Rails,
TypeScript,
Angular 2/4/5,
JavaScript (ES6),
React,
HTML / CSS,
\Gap
Bootstrap,
Foundation,
C,
Swift
\end{large}


%%%%%%%%%%%%%%%%%%%%%%%%%
%% EXPERIENCE %%
%%%%%%%%%%%%%%%%%%%%%%%%%

\BigGap
\Section
{Experience}
{Experience}
{PDF:Experience}

\Entry
\begin{large}
{\textbf{Ikayzo}},
Software Engineer
\hfill
\DatestampYMD{2015}{11}{09} --
Present

\Gap
\BulletItem
Managed \& engineered an ad management and delivery platform extension for Adstream's Japanese market.
\BulletItem
Designed \& developed a web-app for Higa Insurance's taxi auto-insurance management, working with Angular 2 on the front-end and Rails server-side.
\BulletItem
Worked with an international team as a developer on a student loan refinancing Rails and React application for DRB.
\BulletItem
Collaborated closely with the UH Foundation on their online donations application to bring their platform up-to-date and optimize the giving process.
\begingroup % Needed to force word wrap on last bullet point. Refer to sample in the "Journals" section.
\BulletItem
Worked on project proposals, created task estimates in-line with our agile dev practices, and headed design iterations in both project management and development capacities.
\end{large}

\BigGap
\BigGap

\Entry
\begin{large}
{\textbf{IBM}},
Extreme Blue Technical Intern
\hfill
\DatestampYMD{2013}{05}{09} --
\DatestampYMD{2013}{08}{09}

\Gap
\BulletItem
Developed an Android application with a team of interns using agile development practices.
\BulletItem
Created proposals and pitched to IBM executives on a weekly basis.
\BulletItem
Worked with JavaScript, Grails, Vert.x, HTML 5, PhoneGap, and Git, and implemented REST interfaces to design and create the project.
\begingroup % Needed to force word wrap on last bullet point. Refer to sample in the "Journals" section.
\BulletItem
Co-authored four patent submissions internally, of which all were published through IBM.
\end{large}

\BigGap
\BigGap

\Entry
\begin{large}
{\textbf{Virginia Interactive}},
Software Developer Intern
\hfill
\DatestampYMD{2010}{05}{09} --
\DatestampYMD{2012}{08}{09}

\Gap

\BulletItem
\begingroup % Needed to force word wrap on last bullet point. Refer to sample in the "Journals" section.
Pass the Past and Master the Math: Released both as iOS apps, written in Objective-C, as award-winning apps for the Virginia DOE.
\end{large}

%%%%%%%%%%%%%%%
%% EDUCATION %%
%%%%%%%%%%%%%%%

\BigGap
\Section
{Education}
{Education}
{PDF:Education}

\begin{large}
\Entry
{\textbf{Virginia Tech}},

\Gap
B.S. Computer Science with a Minor in Mathematics
\hfill
\DatestampYMD{2011}{08}{15} --
\DatestampYMD{2015}{05}{15}

\BigGap
\Entry
{\textbf{City University of Hong Kong}},

\Gap
Fall 2013 - Education Abroad
\hfill
\DatestampYMD{2013}{08}{15} --
\DatestampYMD{2013}{12}{15}
\end{large}

%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% AWARDS %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%

\BigGap
\Section
{Awards}
{Awards}
{PDF:Awards}

\begin{large}
Computer Science Academic Scholarship recipient for 2012, 2013, 2014
\Gap
Dean’s List for Fall 2011, Spring 2012, Fall 2012, Spring 2013, Spring 2015
\end{large}


%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Languages %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%
\BigGap
\Section
{Languages}
{Languages}
{PDF:Languages}

\begin{large}
English
\textit{(Native)},
Japanese
\textit{(Beginner)},
Spanish
\textit{(Beginner)}
\end{large}

\end{Body}


\end{document}
